Computing solution space properties of combinatorial optimization problems via generic tensor networks

### 2022-08-29 replys/reply.tex
update

\subsection{List of Main Modifications in the Manuscript}\label{header-n30}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item The Section ...
\item A new figure, ...
\item We have added a paragraph at the ...
\item In the revised Supplementary Material, a Section ...
\item In the revised Supplementary Material, the Section ...
\item The section ...
\end{enumerate}

@@

{\bf Response:}
Thank you for the careful reading and constructive comments on notations. We applied the most of the suggested changes accordingly in the main text to make it more readable except the comment 3).
We can not find a better symbol than $\oplus$ to represent the generic plus, so we emphasised this notation is different from the XOR in computer science when we first introduce it.

>>>>

\subsection{List of Main Modifications in the Manuscript}\label{header-n30}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item Define what is a tensor network in Definition 2.1,
\item Define the tensor network representation for all combinatorial optimization problems rigorously in Eq. 4.3 and Appendix B.
\item Add theorems and proofs to the main claims in the paper, including the computation of solution space properties and tensor network contraction complexities in Appendix B.
\end{enumerate}

@@

{\bf Response:}
Thank you for the careful reading and constructive comments on notations. We applied all the suggested changes in the main text except the comment 3).
We can not find a better symbol than $\oplus$ to represent the generic plus, so we emphasised this notation is different from the XOR in computer science when we first introduce it.
